Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
Duplicate label
Saving wrong variable

pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
pseq.genus.core.comp <- microbiome::transform(pseq.genus.core, "compositional")

@@

asine.df <- data.frame()

@@

map_df(res.trim, ~do.call(rbind, .x)) %>%
    dplyr::mutate(Qval = p.adjust(p.value, method="BH")) %>%
    arrange(Qval)

maaslin <- do.call(rbind, lapply(c2l(var.BP), function(BP) res[[BP]]))
saveRDS(maaslin, file = "rds/maaslin.rds")
```

@@

```{r maaslin}
maaslin <- read.table("maaslin1/maaslin/maaslin.txt", header=TRUE, sep='\t')

maaslin %>% filter(Q.value < 0.05)
```

@@

Catabacter, Robinsoniella

```{r compare maaslin to sun, eval = FALSE}
maas.results.df.all <- maaslin$genus %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  Feature = gsub("_Bacteria", "", Feature),
                  beta = Coefficient)

maas.results.df.all %>% pull(Feature) %>% sort %>% unique %>% mygrep("Robin", .)

genus.taxa <- pseq.genus.core %>% abundances %>% rownames

genus.taxa %>% mygrep("Catabacter", .)

maaslin.test <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE",
                                               "HYPERTENSION"),
                                    forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                                               "DIAB", "BL_USE_RX_C03",
                                               "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                               taxa = paste(c("Faecalicatena.Bacteria",
                                        "Catabacter.Bacteria",
                                        "Robinsoniella.Bacteria"), collapse = ", "))

>>>>

if (!file.exists("rds/maaslin.rds")) {
    pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
    pseq.genus.core.comp <- microbiome::transform(pseq.genus.core, "compositional")

@@

@@

    maaslin <- map_df(res.trim, ~do.call(rbind, .x)) %>%
        dplyr::mutate(Qval = p.adjust(p.value, method="BH")) %>%
        arrange(Qval)

@@

@@
